Preparing your manuscript

### 2024-03-14 paper/paper.qmd
Update paper

River runoff is an important component of the global water cycle as it comprises about one third of the precipitation over land areas (Hagemann, 2020). Moreover, accurate runoff forecasting, especially over extended periods, is pivotal for effective water resources management, as highlighted by studies such as Yang et al. (2018), Tan et al. (2018), and Fang et al. (2019).

Over the past decades, models for long-term runoff forecasting have been primarily bifurcated into physically based models and data-based models. While the former attempts to emulate intricate and nonlinear physical hydrological processes, the latter hinges on establishing statistical models that delineate the relationship between large-scale climate patterns and catchment runoff.

Machine Learning (ML) models, such as those employing artificial neural networks, support vector machines, adaptive neuro-fuzzy inference systems, and notably, Long Short-Term Memory (LSTM) neural networks, have gained traction for long-term hydrological forecasting due to their commendable performance (Humphrey et al 2016, Huang et al 2014, Ashrafi et al 2017, Yuan et al 2018, Xu et al 2021).

LSTM networks, an evolution of the classical Recurrent Neural Networks (RNNs), have shown stability and efficacy in sequence-to-sequence predictions, such as using climatic indices for rainfall estimation or long-term hydrological forecasting. However, a limitation of LSTMs is their inability to effectively capture two-dimensional structures, an area where Convolutional Neural Networks (CNNs) excel. Recognizing this, we introduce the ConvLSTM, which integrates the strengths of both LSTM and CNN, to extract spatiotemporal features from precipitation fields for predicting river runoff in the Baltic Sea catchment, summarized by 97 inidivual rivers.

@@

- $x_t$: Input vector at time step $t$.
- $h_{t-1}$: Hidden state from the previous time step.
- $C_{t-1}$: Cell state from the previous time step.
- $W$ and $b$: Weight matrices and bias vectors, respectively, associated with the gates of the LSTM. The subscripts denote the specific gate or operation they are associated with (e.g., $W_f$ and $b_f$ are the weight matrix and bias for the forget gate, respectively).
- $\sigma$: Sigmoid activation function, which squashes values between 0 and 1.
- $\tanh$: Hyperbolic tangent activation function, which squashes values between -1 and 1

@@

@@

| Parameter name | Parameter size | 
|------|------|
| Num. timesteps     | 32    |
| Conv. Kernelsize    | (7,7)    |
| Num. ConvLSTM layers    | 4    |
| Batch size| 32 |
| Learning Rate | 1e-4 with CosineAnnealing |

>>>>

River runoff is an important component of the global water cycle as it comprises about one third of the precipitation over land areas [@hagemannHighResolutionDischarge2020]. For the Baltic Sea river runoff is even more important, as the Baltic Sea is nearly decoupled from the open ocean (see Figure). As a consequence, the salinity of the Baltic Sea is driven to a large part by freshwater supply from rivers. More generally, the freshwater input into the Baltic Sea comes either as river runoff or a positive net precipitation (precipitation minus evaporation) over the sea surface. The net precipitation accounts for 11 \% and the river input for 89 \% of the total freshwater input (Meier and Doescher, 2002). Modeling the Baltic Sea is therefore to a large part the result of the quality of the river input, that is used for the simulation.

In the context of climate change studies, river runoff is usually generated in two ways. First, river runoff as input for ocean models can be created using hyrdological models such as the Hydrological Discharge (HD) model [@hagemannHighResolutionDischarge2020]. HD calculates the water balance using hydrological processes (e.g. snow, glaciers, soil moisture, groundwater contribution). It represents a complex forecast tool that uses underlying physical processes. A different approach would use data-based models that intergrate statistical correction, using the land surface schemes of global or regional climate models.

The releatively recent rise of machine learning (ML) models has been mostly explored for river runoff forcasting, as accurate runoff forecasting, especially over extended periods, is pivotal for effective water resources management [@fangExaminingApplicabilityDifferent2019;@tanAdaptiveMiddleLongterm2018;@yangDerivingOperatingRules2018]. Common approach us employ artificial neural networks, support vector machines, adaptive neuro-fuzzy inference systems, and notably, Long Short-Term Memory (LSTM) neural networks and have gained traction for long-term hydrological forecasting due to their commendable performance (Humphrey et al 2016, Huang et al 2014, Ashrafi et al 2017, Yuan et al 2018, Xu et al 2021).

LSTM networks, an evolution of the classical Recurrent Neural Networks (RNNs), have shown stability and efficacy in sequence-to-sequence predictions, such as using climatic indices for rainfall estimation or long-term hydrological forecasting. However, a limitation of LSTMs is their inability to effectively capture two-dimensional structures, an area where Convolutional Neural Networks (CNNs) excel.

Recognizing this, we use the ConvLSTM, which integrates the strengths of both LSTM and CNN, to extract spatiotemporal features from atmospheric fields for predicting river runoff in the Baltic Sea catchment, summarized by 97 inidivual rivers.

Following the previous description of the complex hyrdological model E-Hype - when present E-Hype should be used. However, in absence of a fully functioning hydrogolocial model, that also uses a rather complex parametrization, RNNs represent a robust way to predict river runoff for any give period of time using atmospheric forcing.

@@

- $x_t$: Input vector at time step $t$.
- $h_{t-1}$: Hidden state from the previous time step.
- $C_{t-1}$: Cell state from the previous time step.
- $W$ and $b$: Weight matrices and bias vectors, respectively, associated with the gates of the LSTM. The subscripts denote the specific gate or operation they are associated with (e.g., $W_f$ and $b_f$ are the weight matrix and bias for the forget gate).
- $\sigma$: Sigmoid activation function ($0,\ldots 1$)
- $\tanh$: Hyperbolic tangent activation function ($ -1 \ldots 1$)

@@

An overview of the model structure is given below

![BaltConvLSTM](model_structure.png){#fig-baltNet}

@@

| Parameter name | Parameter size | 
|------|------|
| Channel size | 4 |
| Num. hidden layer |10 |
| Num. timesteps     | 30    |
| Conv. Kernelsize    | (9,9)    |
| Num. ConvLSTM layers    | 1    |
| Batch size| 64 |
| Learning Rate | 1e-3 with CosineAnnealing |

### 2024-03-14 paper/paper.tex
Update paper

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Preparing your manuscript},
  pdfauthor={Florian Börgel; Sven Karsten},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Preparing your manuscript}
\author{Florian Börgel \and Sven Karsten}
\date{9/29/23}

\begin{document}
\maketitle
\begin{abstract}
The abstract (1) states the nature of the investigation and (2)
summarizes the important conclusions. The abstract should be suitable
for indexing. Your abstract should:
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, enhanced, frame hidden, borderline west={3pt}{0pt}{shadecolor}, interior hidden, boxrule=0pt, sharp corners]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

River runoff is an important component of the global water cycle as it
comprises about one third of the precipitation over land areas
(Hagemann, 2020). Moreover, accurate runoff forecasting, especially over
extended periods, is pivotal for effective water resources management,
as highlighted by studies such as Yang et al.~(2018), Tan et al.~(2018),
and Fang et al.~(2019).

Over the past decades, models for long-term runoff forecasting have been
primarily bifurcated into physically based models and data-based models.
While the former attempts to emulate intricate and nonlinear physical
hydrological processes, the latter hinges on establishing statistical
models that delineate the relationship between large-scale climate
patterns and catchment runoff.

Machine Learning (ML) models, such as those employing artificial neural
networks, support vector machines, adaptive neuro-fuzzy inference
systems, and notably, Long Short-Term Memory (LSTM) neural networks,
have gained traction for long-term hydrological forecasting due to their
commendable performance (Humphrey et al 2016, Huang et al 2014, Ashrafi
et al 2017, Yuan et al 2018, Xu et al 2021).

LSTM networks, an evolution of the classical Recurrent Neural Networks
(RNNs), have shown stability and efficacy in sequence-to-sequence
predictions, such as using climatic indices for rainfall estimation or
long-term hydrological forecasting. However, a limitation of LSTMs is
their inability to effectively capture two-dimensional structures, an
area where Convolutional Neural Networks (CNNs) excel. Recognizing this,
we introduce the ConvLSTM, which integrates the strengths of both LSTM
and CNN, to extract spatiotemporal features from precipitation fields
for predicting river runoff in the Baltic Sea catchment, summarized by
97 inidivual rivers.

@@

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

\hypertarget{lstm-network}{%
\subsubsection{LSTM network}\label{lstm-network}}

@@

\begin{itemize}
\tightlist
\item
  \(x_t\): Input vector at time step \(t\).
\item
  \(h_{t-1}\): Hidden state from the previous time step.
\item
  \(C_{t-1}\): Cell state from the previous time step.
\item
  \(W\) and \(b\): Weight matrices and bias vectors, respectively,
  associated with the gates of the LSTM. The subscripts denote the
  specific gate or operation they are associated with (e.g., \(W_f\) and
  \(b_f\) are the weight matrix and bias for the forget gate,
  respectively).
\item
  \(\sigma\): Sigmoid activation function, which squashes values between
  0 and 1.
\item
  \(\tanh\): Hyperbolic tangent activation function, which squashes
  values between -1 and 1
\end{itemize}

\hypertarget{convlstm-network}{%
\subsubsection{ConvLSTM network}\label{convlstm-network}}

@@

\hypertarget{implemented-model-architecture}{%
\subsubsection{Implemented model
architecture}\label{implemented-model-architecture}}

@@

@@

\hypertarget{tbl-letters}{}
\begin{longtable}[]{@{}ll@{}}
\caption{\label{tbl-letters}Hyperparameters}\tabularnewline
\toprule()
Parameter name & Parameter size \\
\midrule()
\endfirsthead
\toprule()
Parameter name & Parameter size \\
\midrule()
\endhead
Num. timesteps & 32 \\
Conv. Kernelsize & (7,7) \\
Num. ConvLSTM layers & 4 \\
Batch size & 32 \\
~Learning Rate & 1e-4 with CosineAnnealing \\
\bottomrule()
\end{longtable}

\hypertarget{acknowledgments}{%
\subsection{Acknowledgments}\label{acknowledgments}}

@@

\hypertarget{open-research}{%
\subsection{Open research}\label{open-research}}

@@

\hypertarget{references}{%
\subsection*{References}\label{references}}
\addcontentsline{toc}{subsection}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{agujournal2019}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
\usepackage{soul}
\linenumbers
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Preparing your manuscript},
  pdfauthor={Florian Börgel; Sven Karsten},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\journalname{Geophysical Research Letters}

\draftfalse

\begin{document}
\title{Preparing your manuscript}

\authors{Florian Börgel\affil{1}, Sven Karsten\affil{1}}
\affiliation{1}{Leibniz-Institute for Baltic Sea Research Warnemünde, }
\correspondingauthor{Florian Börgel}{florian.boergel@io-warnemuende.de}

\begin{abstract}
The abstract (1) states the nature of the investigation and (2)
summarizes the important conclusions. The abstract should be suitable
for indexing. Your abstract should:
\end{abstract}

\section*{Plain Language Summary}
A Plain Language Summary (PLS) can be an incredibly effective science
communication tool. By summarizing your paper in non-technical terms,
you can explain your research and its relevance to a much broader
audience. A PLS is required for submissions to AGU Advances, G-Cubed,
GeoHealth, GRL, JAMES, JGR: Biogeosciences, JGR: Oceans, JGR: Planets,
JGR: Solid Earth, JGR: Atmospheres, Space Weather, and Reviews of
Geophysics, but optional for other journals. A PLS should be no longer
than 200 words and should be free of jargon, acronyms, equations, and
any technical information that would be unknown to people from outside
your scientific discipline. Read our tips for creating an effective PLS.

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, sharp corners, interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

River runoff is an important component of the global water cycle as it
comprises about one third of the precipitation over land areas (Hagemann
et al., 2020). For the Baltic Sea river runoff is even more important,
as the Baltic Sea is nearly decoupled from the open ocean (see Figure).
As a consequence, the salinity of the Baltic Sea is driven to a large
part by freshwater supply from rivers. More generally, the freshwater
input into the Baltic Sea comes either as river runoff or a positive net
precipitation (precipitation minus evaporation) over the sea surface.
The net precipitation accounts for 11 \% and the river input for 89 \%
of the total freshwater input (Meier and Doescher, 2002). Modeling the
Baltic Sea is therefore to a large part the result of the quality of the
river input, that is used for the simulation.

In the context of climate change studies, river runoff is usually
generated in two ways. First, river runoff as input for ocean models can
be created using hyrdological models such as the Hydrological Discharge
(HD) model (Hagemann et al., 2020). HD calculates the water balance
using hydrological processes (e.g.~snow, glaciers, soil moisture,
groundwater contribution). It represents a complex forecast tool that
uses underlying physical processes. A different approach would use
data-based models that intergrate statistical correction, using the land
surface schemes of global or regional climate models.

The releatively recent rise of machine learning (ML) models has been
mostly explored for river runoff forcasting, as accurate runoff
forecasting, especially over extended periods, is pivotal for effective
water resources management (Fang et al., 2019; Tan et al., 2018; Yang et
al., 2018). Common approach us employ artificial neural networks,
support vector machines, adaptive neuro-fuzzy inference systems, and
notably, Long Short-Term Memory (LSTM) neural networks and have gained
traction for long-term hydrological forecasting due to their commendable
performance (Humphrey et al 2016, Huang et al 2014, Ashrafi et al 2017,
Yuan et al 2018, Xu et al 2021).

LSTM networks, an evolution of the classical Recurrent Neural Networks
(RNNs), have shown stability and efficacy in sequence-to-sequence
predictions, such as using climatic indices for rainfall estimation or
long-term hydrological forecasting. However, a limitation of LSTMs is
their inability to effectively capture two-dimensional structures, an
area where Convolutional Neural Networks (CNNs) excel.

Recognizing this, we use the ConvLSTM, which integrates the strengths of
both LSTM and CNN, to extract spatiotemporal features from atmospheric
fields for predicting river runoff in the Baltic Sea catchment,
summarized by 97 inidivual rivers.

Following the previous description of the complex hyrdological model
E-Hype - when present E-Hype should be used. However, in absence of a
fully functioning hydrogolocial model, that also uses a rather complex
parametrization, RNNs represent a robust way to predict river runoff for
any give period of time using atmospheric forcing.

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{lstm-network}{%
\subsection{LSTM network}\label{lstm-network}}

@@

\begin{itemize}
\tightlist
\item
  \(x_t\): Input vector at time step \(t\).
\item
  \(h_{t-1}\): Hidden state from the previous time step.
\item
  \(C_{t-1}\): Cell state from the previous time step.
\item
  \(W\) and \(b\): Weight matrices and bias vectors, respectively,
  associated with the gates of the LSTM. The subscripts denote the
  specific gate or operation they are associated with (e.g., \(W_f\) and
  \(b_f\) are the weight matrix and bias for the forget gate).
\item
  \(\sigma\): Sigmoid activation function (\(0,\ldots 1\))
\item
  \(\tanh\): Hyperbolic tangent activation function (\$-1 \ldots1)
\end{itemize}

\hypertarget{convlstm-network}{%
\subsection{ConvLSTM network}\label{convlstm-network}}

@@

\hypertarget{implemented-model-architecture}{%
\subsection{Implemented model
architecture}\label{implemented-model-architecture}}

@@

An overview of the model structure is given below

{\centering \includegraphics{model_structure.png}

\caption{\label{fig-baltNet}BaltConvLSTM}

@@

\hypertarget{tbl-letters}{}
\begin{longtable}[]{@{}ll@{}}
\caption{\label{tbl-letters}Hyperparameters}\tabularnewline
\toprule()
Parameter name & Parameter size \\
\midrule()
\endfirsthead
\toprule()
Parameter name & Parameter size \\
\midrule()
\endhead
Channel size & 4 \\
Num. hidden layer & 10 \\
Num. timesteps & 30 \\
Conv. Kernelsize & (9,9) \\
Num. ConvLSTM layers & 1 \\
Batch size & 64 \\
~Learning Rate & 1e-3 with CosineAnnealing \\
\bottomrule()
\end{longtable}

\hypertarget{acknowledgments}{%
\section{Acknowledgments}\label{acknowledgments}}

@@

\hypertarget{open-research}{%
\section{Open research}\label{open-research}}

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\vspace{1em}

\leavevmode\vadjust pre{\hypertarget{ref-fangExaminingApplicabilityDifferent2019}{}}%
Fang, W., Huang, S., Ren, K., Huang, Q., Huang, G., Cheng, G., \& Li, K.
(2019). Examining the applicability of different sampling techniques in
the development of decomposition-based streamflow forecasting models.
\emph{Journal of Hydrology}, \emph{568}, 534--550.
\url{https://doi.org/10.1016/j.jhydrol.2018.11.020}

\leavevmode\vadjust pre{\hypertarget{ref-hagemannHighResolutionDischarge2020}{}}%
Hagemann, S., Stacke, T., \& Ho-Hagemann, H. T. M. (2020). High
{Resolution Discharge Simulations Over Europe} and the {Baltic Sea
Catchment}. \emph{Frontiers in Earth Science}, \emph{8}.
\url{https://doi.org/10.3389/feart.2020.00012}

\leavevmode\vadjust pre{\hypertarget{ref-tanAdaptiveMiddleLongterm2018}{}}%
Tan, Q.-F., Lei, X.-H., Wang, X., Wang, H., Wen, X., Ji, Y., \& Kang,
A.-Q. (2018). An adaptive middle and long-term runoff forecast model
using {EEMD-ANN} hybrid approach. \emph{Journal of Hydrology},
\emph{567}, 767--780.
\url{https://doi.org/10.1016/j.jhydrol.2018.01.015}

\leavevmode\vadjust pre{\hypertarget{ref-yangDerivingOperatingRules2018}{}}%
Yang, Z., Liu, P., Cheng, L., Wang, H., Ming, B., \& Gong, W. (2018).
Deriving operating rules for a large-scale hydro-photovoltaic power
system using implicit stochastic optimization. \emph{Journal of Cleaner
Production}, \emph{195}, 562--572.
\url{https://doi.org/10.1016/j.jclepro.2018.05.154}

\end{CSLReferences}
